A Standard for the Scholarly Citation of Archaeological Data

### 2017-09-06 analysis/paper/paper.Rmd
add in some stuff previously deleted

---
title: "A Standard for the Scholarly Citation of Archaeological Data"
author:
  - "Ben Marwick"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

@@

>>>>

---
title: "A Standard for the Scholarly Citation of Archaeological Data"
author:
  - "Ben Marwick"
  - "Suzanne E. Pilaar Birch"
  - 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
    fig_caption: yes
    reference_docx: templates/template.docx
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

<!-- 
In the pilot studies reported above we see three common approaches to sharing data: sending files privately by email, following a personal request; including data as supplementary files submitted for publication with a journal article; and sharing data by depositing files in a trustworthy, public, DOI-issuing repository. The third method, via a public repository, is by far the most widely recommended method both specifically by archaeologists (Kintigh 2006; Kansa et al. 2011; Kansa and Kansa 2013), and in other sciences (cf. Cranston et al. 2014; Penev et al. 2017; Mounce 2014; Thessen & Patterson 2011; Whitlock 2011).		
 -		
 -		
 -Several guides with detailed information relevant to preparing archaeological data for sharing on a repository. 		
 -		
 -- http://guides.archaeologydataservice.ac.uk/		
 -- http://archaeologydataservice.ac.uk/arches/Wiki.jsp?page=ARCHES%20Introduction		
 -		
 -- http://www.icpsr.umich.edu/files/ICPSR/access/dataprep.pdf		
 -- https://www.dataone.org/sites/all/documents/DataONE_BP_Primer_020212.pdf		
 -- http://www.data-archive.ac.uk/media/2894/managingsharing.pdf
 -->

@@

<!---
-In-text citation:

 “This paper uses data from the [name] data repository at https://doi.org/***** (Jones et al. 2008a), first described in Jones et al. 2008b. “

 Data reference and article reference in reference list:

 Jones A, Bloggs B, Smith C (2008a). <Title of data package>. <Repository name>. doi: https://doi.org/#####. [Version and/or date of access].
 -->
